Uncovering Distributed System Bugs\\ during Testing (not Production!) -- draft title

### 2015-08-16 paper.tex
added background text on P#
update in abstract

\usepackage{xspace}

@@

\maketitle
\begin{abstract}
Distributed systems are notoriously hard to test. This is due to many well-known sources of nondeterminism: races in the asynchronous interaction between system components; the use of multithreaded code inside individual components; unexpected node failures; message losses; and interaction with a complex external environment. Stress testing techniques that are commonly used in industry are unable to effectively capture and control all these sources of nondeterminism, which causes many tricky bugs to be missed during testing and only get exposed after a system has been put in production.

@@

Distributed systems are notoriously hard to test. This is due to many well-known sources of nondeterminism: races in the asynchronous interaction between system components; the use of multithreaded code inside individual components; unexpected node failures; message losses; and interaction with a complex external environment. Stress testing techniques that are commonly used in industry are unable to effectively capture and control all these sources of nondeterminism, which causes many tricky bugs to be missed during testing and only get exposed after a system has been put in production.

@@

Easy to think you can do better until it happens to you :-)

@@

\section{Conclusions}
\label{sec:concl}

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns

>>>>

\usepackage{url}
\usepackage{xspace}

@@

\maketitle
\begin{abstract}
Distributed systems are notoriously hard to test. This is due to many well-known sources of nondeterminism: races in the asynchronous interaction between system components; the use of multithreaded code inside individual components; unexpected node failures; message losses; and interaction with a complex external environment. Stress testing techniques, commonly used in industry today, are unable to capture and control all these sources of nondeterminism. This results in many tricky bugs be missed during testing and only get exposed after a system has been put in production.

@@

\input{intro}

@@

\input{background}

@@

\input{related}

\section{Conclusion}
\label{sec:concl}

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{references}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
